---
title: "Version 4: Customize"
author: "Jenna Landy"
output:
  rmdformats::robobook
params:
  package_location: 
    label: "Path to Iris Project Package:"
    value: "./irisproject/"
    input: text
  convert_cm: 
    label: "Convert Centimeters to Inches?"
    value: TRUE
  plot_pairs_of: 
    label: "Variables to Include in Pairs Plot (comma separated):"
    value: "Sepal.Length, Sepal.Width, Petal.Length, Petal.Width, Length.Ratio, Width.Ratio, Circumference, Species"
    input: text
---

```{css, echo = FALSE}
.book {
  padding-top: 40px
}


.book .book-body .page-inner section.normal h1, .book .book-body .page-inner section.normal h2, .book .book-body .page-inner section.normal h3, .book .book-body .page-inner section.normal h4 {
  padding-top: 40px
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

rm(list = c('iris'))
```

# Setup  {.tabset .tabset-fade .tabset-pills}

## Packages
```{r}
# use install.packages FIRST TIME ONLY
update.packages(
  params$package_location,
  repos=NULL,
  type="source"
)

library(irisproject)
library(dplyr)
library(ggplot2)
library(plotly)
```

## Parameters
```{r}
for (p in names(params)) {
  print(paste0(p, ': ', params[[p]]))
}
```

# Starting Data

```{r}
head(iris) %>%
  knitr::kable(digits = 3)
```

# Data Manipulation {.tabset .tabset-fade .tabset-pills}

`r if(params$convert_cm) {"## Convert Measurements"}`
`r if(params$convert_cm) {"Converting data in first four columns from centemeters to inches"}`
```{r include = params$convert_cm}
if (params$convert_cm) {
  iris <- iris %>%
  convert_measurements(1:4)
}
```

##  Ratio features
Computing two ratio features: ratio of lengths (sepal : petal) and ratio of widths (sepal : petal)
```{r}
iris <- iris %>%
  compute_ratios()
```

## Circumference
Creating a new feature: circumference of the smallest circle that could circumscribe the flower (using the larger length as the radius).
```{r}
iris <- iris %>%
  compute_circumference()
```

# Final Data

```{r}
head(iris) %>%
  knitr::kable(digits = 3)
```

# Plots

## Pairs plot of select variables

```{r}
plot_pairs_of <- strsplit(params$plot_pairs_of, ",")[[1]] %>% trimws()
```

```{r results="asis", echo= FALSE}
cat(knitr::asis_output("Variables included:\n\n"))
for (var in plot_pairs_of) {
  cat(knitr::asis_output(paste0(
    "- ",
    var,
    "\n"
  )))
}
```

```{r}
pairs(iris[,plot_pairs_of])
```

## Plot of circumference and length ratio by species

```{r}
p <- iris %>% ggplot(aes(
  x = Circumference, 
  y = Length.Ratio, 
  color = Species,
  text = paste0(
    "Species: ", Species,
    "\nCircumference: ", round(Circumference,3),
    "\nLength Ratio: ", round(Length.Ratio, 3),
    "\nWidth Ratio: ", round(Width.Ratio, 3),
    "\nPetal Width, Length: ", round(Petal.Width, 3),
        ", ", round(Petal.Length, 3),
    "\nSepal Width, Length: ", round(Sepal.Width, 3),
        ", ", round(Sepal.Length, 3)
  )
)) +
  geom_point() +
  theme_classic() +
  theme(
    legend.position = 'top',
    legend.justification = 'left'
  )

plotly::ggplotly(p, tooltip = c("text")) %>%
  plotly::layout(
    legend = list(
      orientation = "h",
      x = 0,
      yanchor = "bottom",
      y = 1.02
    )
  )
```


